---
title: "Data Wrangling Exercise 2"
output: html_document
---

## Add R Packages
```{r}
library("dplyr", lib.loc="/Library/Frameworks/R.framework/Versions/3.4/Resources/library")
library("tidyr", lib.loc="/Library/Frameworks/R.framework/Versions/3.4/Resources/library")
library("readr", lib.loc="/Library/Frameworks/R.framework/Versions/3.4/Resources/library")
```

## Import Data
```{r}
library(readr)
titanic_original <- read_csv("~/Desktop/titanic_original.csv")
View(titanic_original)
```

## Port of Embarkation
```{r}
is.na(titanic_original$embarked)
titanic_original$embarked <- gsub("NA", "S", titanic_original$embarked)
```

## Age - Performing mean age as per the instructions but also evaluating how median age might provide a different replacement value
```{r}
mean_age <- mean(titanic_original$age, na.rm = TRUE)
median_age <- median(titanic_original$age, na.rm = TRUE)
mean_age
median_age
titanic_original$age <- replace(titanic_original$age, is.na(titanic_original$age), mean_age)
```
## Note that median age is slightly lower but not dramatically different as a replacement value.

## Lifeboat
```{r}
na_boat <- which(is.na(titanic_original$boat))
titanic_original$boat[na_boat] <- "None"

```
## Cabin
## It does not make sense to fill in an inaccurate identifier for cabin. A missing value may mean steerage class, crew, etc.
```{r}
titanic_original$has_cabin_number <- as.numeric(!(is.na(titanic_original$cabin)))
```
## Write CSV of new file
```{r}
write.csv(titanic_original, file = "~/Desktop/titanic_clean.csv")
```


